MSB104_assignment1

### 2023-10-03 MSB104_assignment1.qmd
Last update 03.10.23.

```{r}
gdp <- nama_10r_3gdp
```

```{r}
str(gdp)
```

```{r}
countries_to_keep <- c("FI", "DE", "RO")
filtered_data <- gdp %>%
  filter(substr(`unit,geo\\time`, 9, 10) %in% countries_to_keep)
selected_columns <- filtered_data %>%
  select(`unit,geo\\time`, `2000`:`2020`)
```

```{r}
gdp_DE_FI_RO <- selected_columns 
```

>>>>

```{r}
# Change file name nama_10r_3gdp to gdp
gdp <- nama_10r_3gdp
# Filter sorted by provided following contries: Finland (FI), Germany (DE) & Romania (RO). Furthermore, filter selected period 2000:2020.
countries_to_keep <- c("FI", "DE", "RO")
filtered_data <- gdp %>%
  filter(substr(`unit,geo\\time`, 9, 10) %in% countries_to_keep)
selected_columns <- filtered_data %>%
  select(`unit,geo\\time`, `2000`:`2020`)
# Renamed file from selected_colums to gdp_DE_FI_RO
gdp_DE_FI_RO <- selected_columns 
```

```{r}
str(demo_r_pjanaggr3)
```
